---
title: "Initial Exploratory Data Analysis (WIP)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## Exploratory data analysis

We provide high level descriptive statistics on the data. Note that we should refrain from showing detailed information from all but the first few calendar years available before we decide on a validation approach to prevent leakage. The input data has also been scaled to provide further anonymity. Feel free to edit/correct/append or otherwise contribute to this document.

### Summary by LOB

```{r echo = FALSE, message = FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
raw <- read_csv("data/data_f.csv")
lob_summary <- raw %>%
  rename(accident_year = AccidentYear,
         transaction_type = Transaction,
         claim_number = ClaimNb,
         lob = Occupancy,
         reporting_year = ReportingYear,
         cover_type = CoverType,
         status = Status) %>%
  mutate(lob = lob %>%
           gsub("^Lob", "", .) %>%
           str_pad(2, side = "left", pad = "0"),
         calendar_year = accident_year + dev / 12 - 1) %>%
  group_by(lob, cover_type) %>%
  filter(value > 0) %>%
  summarize(first_ay = min(accident_year),
            last_ay = max(accident_year),
            first_cy = min(calendar_year),
            last_cy = max(calendar_year),
            first_ry = min(reporting_year),
            last_ry = max(reporting_year))
```

```{r, echo = FALSE}
DT::datatable(lob_summary)
```