---
title: "Initial Exploratory Data Analysis (WIP)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## Exploratory data analysis

We provide high level descriptive statistics on the data. Note that we should refrain from showing detailed information from all but the first few calendar years available before we decide on a validation approach to prevent leakage. Feel free to edit/correct/append or otherwise contribute to this document.

### Year ranges by LOB

The following table shows the first and last accident year, calendar year, and report years for which transactions exist for each of the LOB.

```{r echo = FALSE, message = FALSE}
library(tidyverse)
data <- read_csv("data/combined_data_full.csv")
lob_summary <- data %>%
  group_by(lob, cover_type) %>%
  filter(value > 0) %>%
  summarize(first_ay = min(accident_year),
            last_ay = max(accident_year),
            first_cy = min(calendar_year),
            last_cy = max(calendar_year),
            first_ry = min(report_year),
            last_ry = max(report_year))
```

```{r, echo = FALSE, result = "asis"}
knitr::kable(lob_summary)
```